\section{Evaluation / Usage}
\label{sec:evaluation}

The final system is a web-based application designed to provide an intuitive, interactive, and accessible platform for creating, visualizing, and simulating graphs and algorithms. This section outlines the system’s features, architecture, and usability, highlighting how the components integrate to deliver the intended functionality.

\subsection{Features}
The system includes the following key features:
\begin{itemize}
    \item \textbf{Graph Builder:} Users can create, edit, and manipulate directed and undirected graphs. Nodes and edges can be added or deleted dynamically, with support for interactive drag-and-drop adjustments.
    \item \textbf{Graph Visualizer:} A dedicated visualizer displays the graph, allowing users to explore its structure and properties interactively.
    \item \textbf{Algorithm Simulations:} Step-by-step visualizations for:
    \begin{itemize}
        \item \textbf{Dijkstra's Algorithm:} Shortest path calculation.
        \item \textbf{Breadth-First Search (BFS):} Level-wise graph traversal.
        \item \textbf{Depth-First Search (DFS):} Recursive graph traversal.
    \end{itemize}
    \item \textbf{Predefined Examples:} Users can load example graphs for exploration, visualization, and algorithm simulation without needing to create graphs from scratch.
    \item \textbf{Responsive User Interface:} The application is accessible through modern web browsers, offering a seamless experience across devices.
\end{itemize}

\subsection{Integration and Workflow}
The system workflow is designed to be user-friendly and intuitive:
\begin{itemize}
    \item Users start by either creating a new graph or loading a predefined example.
    \item The graph builder allows dynamic creation and modification of nodes and edges.
    \item The graph visualizer provides real-time feedback and displays the graph structure interactively.
    \item Users can run algorithm simulations on the graph, observing step-by-step execution and real-time animations.
    \item Users can reset or modify the graph and rerun simulations as needed.
\end{itemize}

\subsection{Usability and Educational Impact}
The system is tailored for educational use, benefiting both students and educators:
\begin{itemize}
    \item \textbf{For Students:} The interactive graph builder and algorithm simulations provide a hands-on learning experience, helping to reinforce theoretical concepts through experimentation.
    \item \textbf{For Educators:} The tool serves as a teaching aid, enabling dynamic demonstrations of graph algorithms and their behavior in real-time.
\end{itemize}
The system’s responsive design ensures accessibility across different devices, making it suitable for classroom use, remote learning, and self-study.

\subsection{Limitations and Future Enhancements REDUNDANT, MAKE PART OF FUTURE WORK}
While the system achieves its primary goals, there are some limitations:
\begin{itemize}
    \item \textbf{Scalability:} Performance may degrade with very large graphs due to browser limitations.
    \item \textbf{Algorithm Coverage:} Currently, only a subset of graph algorithms is implemented (Dijkstra, BFS, DFS). Expanding the algorithm library would enhance the system’s utility.
    \item \textbf{Backend Integration:} The application is entirely frontend-based, and adding backend support could enable features such as saving/loading graphs or collaborative editing.
\end{itemize}
These limitations offer opportunities for future improvements and extensions to the system.

\subsection{Summary REDUNDANT, OWN CHAPTER}
The final system provides an effective and versatile platform for exploring graph theory and algorithms interactively. Its modular architecture, dynamic features, and educational focus make it a valuable tool for students and educators alike. By combining flexibility, usability, and interactivity, the application bridges the gap between theoretical knowledge and practical learning in graph-based concepts.
