\section{Implementation}
\label{sec:implementation}

\subsection{Early Exploration}
The development process began with an exploration of available tools for graph visualization. Initial prototyping was conducted using Graphviz, a popular tool for static graph rendering. While Graphviz proved effective for creating static visualizations, it posed significant limitations for this project:
\begin{itemize}
    \item Lack of interactivity and flexibility required for dynamic visualization and user interaction.
    \item Limited compatibility with modern web technologies for building highly interactive applications.
\end{itemize}
As a result, the decision was made to switch to \textbf{D3.js}, a JavaScript library that offers robust support for dynamic and interactive graph rendering. Despite its steep learning curve, D3.js provided the flexibility and control needed to meet the project’s requirements. Early experimentation focused on understanding its core concepts, including data binding, SVG manipulation, and event handling.

\subsection{Stepwise Implementation}

\subsubsection{Prototype Graph Builder}
The first implementation step involved creating a basic prototype for the graph builder using D3.js. This included:
\begin{itemize}
    \item Dynamic addition and deletion of nodes and edges.
    \item Learning to manipulate nodes and edges interactively through drag-and-drop functionality.
    \item Initial usability testing to refine the interface and ensure user-friendly interactions.
\end{itemize}

\subsubsection{Directed and Undirected Graph Creation}
Following the prototype, support for both directed and undirected graphs was implemented. Key considerations included:
\begin{itemize}
    \item Visual differentiation between directed and undirected edges.
    \item Functional adjustments to ensure the correct handling of graph types in algorithms.
    \item Enhancements to the user interface for toggling between directed and undirected graphs.
\end{itemize}

\subsubsection{Graph Visualizer}
The next step was the development of a dedicated visualization component to display and interact with graphs. Features implemented included:
\begin{itemize}
    \item Interactive manipulation of nodes and edges.
    \item Real-time updates to the graph as modifications were made.
    \item Initial integration of graph traversal highlighting to support future algorithm simulations.
\end{itemize}

\subsubsection{Algorithm Simulations (Dijkstra, BFS, DFS)}
With the visualizer in place, algorithm simulation functionality was added:
\begin{itemize}
    \item Step-by-step execution of Dijkstra’s algorithm to visualize the shortest path.
    \item BFS and DFS traversal simulations to demonstrate graph exploration.
    \item Integration with the visualizer to highlight nodes and edges during algorithm execution.
\end{itemize}
Special attention was given to making the simulations user-friendly by providing controls for pausing, resuming, and resetting the algorithms.

\subsubsection{Integration of Predefined Examples}
To showcase the application’s capabilities, predefined example graphs were integrated. These examples allow users to:
\begin{itemize}
    \item Load ready-made graphs directly into the builder or visualizer.
    \item Experiment with algorithm simulations without needing to create graphs from scratch.
    \item Explore use cases, such as road networks or tree structures, to understand graph algorithms in context.
\end{itemize}

\subsection{Challenges and Iterations}
The development process involved overcoming several challenges:
\begin{itemize}
    \item \textbf{Learning Curve:} Adapting to D3.js required significant effort, particularly for implementing advanced interactions and animations.
    \item \textbf{Performance Issues:} Handling larger graphs required optimization of rendering and interaction logic to maintain smooth performance.
    \item \textbf{User Interface Design:} Ensuring the application was intuitive and user-friendly involved multiple iterations and feedback from early testers.
\end{itemize}
Each challenge was addressed through iterative development, with frequent testing and refinement to ensure a high-quality final product.
